{\bf Practical Concurrency Testing}

### 2018-10-17 thesis/defense/snakefight.tex
revisions aftre 3am practice to self ;_;

\begin{frame}{Evaluation}
	79 ``P2'' thread libraries from CMU, 78 ``Pintos'' kernels from U. Chicago \& Stanford
	\linegap

	%629 pairs of \{P2 or Pintos\} + test case
	629 pairs of P2 or Pintos + test case
	\linegap

@@

\begin{frame}{Survey}
	14(ish) questions, investigate both education \& happiness
	\begin{itemize}
		\item {\bf Education:} Did Landslide help students learn more from P2?
		\item {\bf Happiness:} Did Landslide help students save time/effort?
	\end{itemize}
	\pause
	\linegap

	Self-report any {\bf false positives}
	\begin{itemize}
		\item Landslide crashes aside, 3 FP bug reports, all simple bugs (now fixed)
			% nonexistent MAGIC_BREAK bc of different address space in shell
			% simultaneous landslides corrupt each other
			% invalid heap access when new_pages "too close"
		\item No FPs related to yield-loop/etc heuristics
	\end{itemize}
	\linegap

\begin{frame}{Survey Results} % (educational value)}
	\begin{center}
		\includegraphics[width=\textwidth]{../survey6.pdf} % easier to diagnose?
	\end{center}
\end{frame}

@@

@@

\breakslide{\Large \bf \hilight{sect-htm}{Transactional Memory}}

@@

	Transaction failure
	\begin{itemize}
		\item Possible reasons:
			\begin{itemize}
				\item Memory conflict with another thread
				\item False sharing (conflict on same cache-line)
				\item Cache eviction, random interrupt, ...
			\end{itemize}
		\item Changes discarded, local state reverted, \xbegin returns failure
		\item {\tt else} branch runs some user-supplied backup plan
	\end{itemize}
\end{frame}

@@

\begin{frame}{Concurrency model}
	What are a transactional program's {\em observable} behaviours?
	\begin{itemize}
		\item Transactional writes, if successful, appear atomically %to other threads
		%\begin{itemize}
		%	\item Equivalent to a lock protecting that state
		%		% note that also inserting DR PPs within a transaction is not allowed
		%\end{itemize}
		%	\pause
		\item Simultaneous transactions succeed only if no conflicts
		%\begin{itemize}
		%	\item Equivalent
		%		%(modulo performance)
		%		to serialize independent transactions
		%\end{itemize}
		%	\pause
		\item Failing transactions' effects rolled-back with no trace
		%\begin{itemize}
		%	\item Treat each \xbegin as a failure injection point
		%\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

	Even simple programs tricky to get right
	\begin{itemize}
		\item Author of {\tt mutex\_is\_locked()} pattern got it wrong once...
		\item Landslide can check even unpredictable performance characteristics
	\end{itemize}
	\linegap

	Abstraction reduction eases both implementation \& verification burden
\end{frame}

@@

\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey1.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey2.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey3.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey4.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey5.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey7.pdf} \end{center} \end{frame}

>>>>

\begin{frame}{Evaluation}
	629 tests of submitted ``P2'' thread libraries (CMU) and ``Pintos'' kernels (U. Chicago \& Stanford)
	%79 ``P2'' thread libraries from CMU, 78 ``Pintos'' kernels from U. Chicago \& Stanford
	\linegap

	%%629 pairs of \{P2 or Pintos\} + test case
	%629 pairs of P2 or Pintos + test case
	%\linegap

@@

\begin{frame}{Survey}
	14(ish) questions, investigate both education \& happiness
	\begin{itemize}
		\item {\bf Education:} Did Landslide help students learn more from P2?
		\item {\bf Happiness:} Did Landslide help students save time/effort?
	\end{itemize}
\end{frame}

@@

\begin{frame}{Survey Results}
	Self-report any {\bf false positives}
	\begin{itemize}
		\item Landslide crashes aside, 3 FP bug reports, all simple bugs (now fixed)
			% nonexistent MAGIC_BREAK bc of different address space in shell
			% simultaneous landslides corrupt each other
			% invalid heap access when new_pages "too close"
		\item No FPs related to yield-loop/etc heuristics
	\end{itemize}
	\pause
	\linegap

@@

\breakslide{\Large \bf \hilight{sect-htm}{Hardware Transactional Memory}}

@@

	Transaction failure
	\begin{itemize}
		\item Possible reasons:
			\begin{itemize}
				\item Memory conflict with another thread
				%\item False sharing (conflict on same cache-line)
				\item Cache conflicts, cache eviction, random interrupt, ...
			\end{itemize}
		\item Changes discarded, local state reverted, \xbegin returns failure
		\item {\tt else} branch runs some user-supplied backup plan
	\end{itemize}
\end{frame}

@@

\begin{frame}{Concurrency model}
	That first {\tt count++} never happened...!
	\linegap

	%What are a transactional program's {\em observable} behaviours?
	%\begin{itemize}
	%	\item Transactional writes, if successful, appear atomically %to other threads
	%	%\begin{itemize}
	%	%	\item Equivalent to a lock protecting that state
	%	%		% note that also inserting DR PPs within a transaction is not allowed
	%	%\end{itemize}
	%	%	\pause
	%	\item Simultaneous transactions succeed only if no conflicts
	%	%\begin{itemize}
	%	%	\item Equivalent
	%	%		%(modulo performance)
	%	%		to serialize independent transactions
	%	%\end{itemize}
	%	%	\pause
	%	\item Failing transactions' effects rolled-back with no trace
	%	%\begin{itemize}
	%	%	\item Treat each \xbegin as a failure injection point
	%	%\end{itemize}
	%\end{itemize}
	%\pause
	%\linegap

@@

	Landslide found surprising bugs in AVL tree, spinlock
	\linegap

	%Even simple programs tricky to get right
	%\begin{itemize}
	%	\item Author of {\tt mutex\_is\_locked()} pattern got it wrong once...
	%	\item Landslide can check even unpredictable performance characteristics
	%\end{itemize}
	%\linegap

	Abstraction reduction eases %both implementation \&
	verification burden
\end{frame}

@@

\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey1.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey2.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey3.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey4.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey5.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey6.pdf} \end{center} \end{frame}
\begin{frame}{Survey Results} \begin{center} \includegraphics[width=\textwidth]{../survey7.pdf} \end{center} \end{frame}
